---
title: "Building the Shinylive App for Canada-U.S. Productivity"
author: "Michael Willox"
format: html
editor: visual
---


## Overview

This document tracks the steps, successes, and failures involved in building and deploying a Shinylive app.

## Folder Structure Setup **Before** Running 'Run_Shinylive_app.R'.

shinylive-cn-us-prdty
├── app.R  
├── df_clean.RDS  
├── docs
│   ├── app.json
│   ├── edit
│   ├── index.html
│   ├── shinylive
│   ├── sinylive-sw.js
└── shinylive-cn-us-prdty.Rproj 


├── app.R  
├── df_clean.RDS  
├── data  
│   ├── cn_us_mfp.csv  
│   ├── cn_us_mfp.RDS  
│   ├── cn_us_mfp.xlsx  
├── prep_data.R  
├── Proceedure.html  
├── Proceedure.qmd  
├── Proceedure.rmarkdown  
├── Proceedure_files  
├── Run_Shinylive_app.R  
└── shinylive-cn-us-prdty.Rproj  


## Folder Structure Setup **After** Running 'Run_Shinylive_app.R'.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(fs)
library(tree)
library(cli)

# Define root (relative or absolute path)
root <- "."

# List files recursively
cat("📁 This is the folder structure for the Shinylive app:\n\n")

files <- fs::dir_tree(path = root, recurse = TRUE, type = "any", n = Inf)
```


```{r, message=FALSE, echo=FALSE, warning=FALSE}

cat("📁 These are the individual files:\n\n")
print(files)
```



shinylive::export(appdir = "app", destdir = "docs")

httpuv::runStaticServer("docs")


- Set up new remote repo
 - https://github.com/MichaelWillox/shinylive-cn-us-prdty
- Open Git
 - cd C:\Users\micha\My_Projects\shinylive-cn-us-prdty
 - git init
 - Link to Your Remote Repo If you haven’t already connected it: 

git remote add origin https://github.com/MichaelWillox/shinylive-cn-us-prdty.git

You can confirm it worked with:
git remote -v

You'll see this:
C:\Users\micha\My_Projects\shinylive-cn-us-prdty>git remote -v
origin  https://github.com/MichaelWillox/shinylive-cn-us-prdty.git (fetch)
origin  https://github.com/MichaelWillox/shinylive-cn-us-prdty.git (push)

# Add and Commit Your Files

git add .
git commit -m "Initial commit: working Shinylive app and docs export"

# Push to GitHub

git branch -M main
git push -u origin main

C:\Users\micha\My_Projects\shinylive-cn-us-prdty>git push -u origin main
To https://github.com/MichaelWillox/shinylive-cn-us-prdty.git
 ! [rejected]        main -> main (fetch first)
error: failed to push some refs to 'https://github.com/MichaelWillox/shinylive-cn-us-prdty.git'
hint: Updates were rejected because the remote contains work that you do
hint: not have locally. This is usually caused by another repository pushing
hint: to the same ref. You may want to first integrate the remote changes
hint: (e.g., 'git pull ...') before pushing again.
hint: See the 'Note about fast-forwards' in 'git push --help' for details.

C:\Users\micha\My_Projects\shinylive-cn-us-prdty>git pull --rebase origin main
remote: Enumerating objects: 3, done.
remote: Counting objects: 100% (3/3), done.
remote: Compressing objects: 100% (2/2), done.
remote: Total 3 (delta 0), reused 0 (delta 0), pack-reused 0 (from 0)
Unpacking objects: 100% (3/3), 1.44 KiB | 105.00 KiB/s, done.
From https://github.com/MichaelWillox/shinylive-cn-us-prdty
 * branch            main       -> FETCH_HEAD
 * [new branch]      main       -> origin/main
Successfully rebased and updated refs/heads/main.

C:\Users\micha\My_Projects\shinylive-cn-us-prdty>git push -u origin main
Enumerating objects: 438, done.
Counting objects: 100% (438/438), done.
Delta compression using up to 12 threads
Compressing objects: 100% (332/332), done.
Writing objects: 100% (437/437), 111.57 MiB | 3.51 MiB/s, done.
Total 437 (delta 17), reused 0 (delta 0), pack-reused 0
remote: Resolving deltas: 100% (17/17), done.
To https://github.com/MichaelWillox/shinylive-cn-us-prdty.git
   1e030a5..0993e62  main -> main
branch 'main' set up to track 'origin/main'.

C:\Users\micha\My_Projects\shinylive-cn-us-prdty>
## What Worked

- Export using `shinylive export app docs`
- Pushing to GitHub repo
- GitHub Pages rendered the app at the correct URL

## What Did Not Work

- Needed to use `ifelse(..., NA_real_)` to avoid divide-by-zero
- Plot legend required `element_text()` for styling
...
